Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-07 tex/main.tex
more

Another useful fragment is the class of \emph{productive} corecursive
functions. Corecursive functions are functions to a coalgebraic datatype.
These functions can call themselves forever, without their being inconsistent.
Productive corecursive functions are functions that progressively reveal parts
of their (potentially infinite)
output \cite{turner-1995,mcbride-productive}.
For example, given a type of infinite streams constructed by $\con{scons}$,
the definition
$\{\forallf{\const{e}} n.\;\, \const{e}(n) \teq \con{scons}(n,\; \const{e}(n + 1))\}$
falls within this fragment, since each call to $\const{e}$ produces one
constructor before entering the nested call. Like terminating recursion,
productive corecursion totally specify the functions it defines. The
following theorem connects totality with admissibility.

\begin{definition}\rm
Let $\DDD$ be a set of function definitions for $\sfundefs{\Sigma}$. The set
$\DDD$ is \emph{total} if for every
$(\stypes{\Sigma},\, \sfuns{\Sigma} - \sfundefs{\Sigma})$-interpretations
$\J_0$, there exists a unique
$\Sigma$-interpretation $\J$ that extends $\J_0$
and for which $\J \models \DDD$.
\end{definition}

>>>>

Another useful fragment is the class of \emph{productive} corecursive
functions. Corecursive functions are functions to a coalgebraic datatype.
These functions can call themselves forever, without their being inconsistent.
Productive corecursive functions are functions that progressively reveal parts
of their (potentially infinite)
output \cite{turner-1995,mcbride-productive}.
For example, given a type of infinite streams constructed by $\con{scons}$,
the definition
$\{\forallf{\const{e}} n.\;\, \const{e}(n) \teq \con{scons}(n,\; \const{e}(n + 1))\}$
falls within this fragment, since each call to $\const{e}$ produces one
constructor before entering the nested call. Like terminating recursion,
productive corecursion totally specify the functions it defines.
It is even possible to mix recursion and corecursion in the same function
\cite{blanchette-et-al-2015-fouco}.

Here, we focus on a fragment of all reasonable recursive--corecursive
specifications, where each function is either well-founded or productive.
Mutual (co)recursion is not catered for, but it can be encoded in terms of
simple (co)recursion.

\begin{definition}
Let $\DDD = \{ \forallf{\con{f}_1} \vec x.\; \varphi_1, \ldots,
\forallf{\con{f}_n} \vec x.\; \varphi_n \}$ be a set of function definitions.
This set forms a \emph{layered }(\emph{co})\emph{recursive specification} if
$\const{f}_i$'s definition may not syntactically refer to $\const{f}_{j}$ for
all $i < j$ and each $\const{f}_i$ is either well-founded recursive
or productive corecursive.
\end{definition}

\begin{definition}\rm
Let $\DDD$ be a set of function definitions for $\sfundefs{\Sigma}$. The set
$\DDD$ is \emph{} if for every
$(\stypes{\Sigma},\, \sfuns{\Sigma} - \sfundefs{\Sigma})$-interpretations
$\J_0$, there exists a unique
$\Sigma$-interpretation $\J$ that extends $\J_0$
and for which $\J \models \DDD$.
\end{definition}
